Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions

### 2017-01-27 writing/phase_transition/phase_transition.tex
Non-symmetric barrier done

This paper is arranged as follows.
In Sec. \ref{sec:model} we explain in details our model to realize Josephson junction with exciton polariton condensates.
The extended tight-binding model will be established in this case.
In Sec. \ref{sec:quantum_phase} we \dots.
In the conclusion, we summarize the results obtained.

@@

\textit{Josephson regime} $1/N^2\ll\Lambda <1$.
This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
The behavior of the phase depends on the ratio between parameters $\Lambda$ and $\lambda$.
If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like {\red equation for small oscillations}.

@@

Expansion of the potential $V(z)$ excluding constant value $V(0)$ gives:
%
\begin{equation}
\begin{array}{lcl}
V_0(z) & = &\left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (1 - \lambda) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
\end{array}
\label{eq:potential_teylor}
\end{equation}
%
In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the first order phase transition occurs.
If $-V(z)$ behaves as $z^2 + z^4$ second order phase transition take place.
Phase boundary between 1st and 2nd order phase transition is determined by the relation
%
\begin{equation}
\Lambda = \frac{1 - 16\lambda + 16\lambda^2 + \sqrt{1 + 32\lambda - 32\lambda^2}}{4(2\lambda - 1)}.
\label{eq:order_border}
\end{equation}
%
We summarize our results in the Fig.\ref{pic:phase_boundary}. 
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$, $\lambda$ - parameter plane. \label{pic:phase_boundary}}
\end{figure}
%

@@

>>>>

This paper is arranged as follows.
In Sec. \ref{sec:model} we explain in details our model to realize Josephson junction with exciton polariton condensates.
The extended tight-binding model will be established in this case.
In Sec. \ref{sec:quantum_phase} we {\red \dots }.
In the conclusion, we summarize the results obtained.

@@

\textit{Josephson regime} $1/N^2\ll\Lambda <1$.
This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
The behavior of the phase depends on the ratio between parameters $\Lambda$ and $\lambda$.
If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like { \red $\omega_{0, quantum} = 2 \alpha s \sqrt{\frac{1}{4} \Lambda^2 - \frac{\Lambda}{2} (2\lambda - 1) - \lambda(1 - \lambda)}$ }.

@@

Expansion of the potential $V(z)$ excluding constant value $V(0)$ gives:
%
\begin{equation}
\begin{array}{lcl}
V(z) & = & \alpha s^2 \Big[ \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (1 - \lambda) (2\lambda - 1)}{3} \right) z^4 + o(z^4) \Big].
\end{array}
\label{eq:potential_teylor}
\end{equation}
%
In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the first order phase transition occurs.
If $-V(z)$ behaves as $z^2 + z^4$ second order phase transition take place.
Phase boundary between 1st and 2nd order phase transition is determined by the relation
%
\begin{equation}
\Lambda = \frac{1 - 16\lambda + 16\lambda^2 + \sqrt{1 + 32\lambda - 32\lambda^2}}{4(2\lambda - 1)}.
\label{eq:order_border}
\end{equation}
%
We summarize our results in the Fig.\ref{pic:phase_boundary}. 
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$, $\lambda$ - parameter plane. \label{pic:phase_boundary}}
\end{figure}
%

@@

{\red

Another type of barrier --- upper barrier.
Exist when $\Lambda > 2(1 - \lambda)$.
Potential presumes local minima at $\pm 2K(\lambda)$ and local maxima at $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
Equation for the thermon yeilds small ocsilation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \alpha s \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
The crossover temperature of second-order phase transition
%
\begin{equation}
T_{c}^{(2)} = (\hbar \alpha s / 2 \pi k_B) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}.
\label{eq:second_order_2}
\end{equation}
%
With the aim of analytical determining of the phase transition order let's write the Taylor series for $V(z)$ near the vicinity of $z_{max}$.
Expansion of the potential $V(z)$ excluding constant value $V(z_{max})$ gives:
%
\begin{equation}
V(\tilde{z}) = \alpha s^2 \Big[ -\tfrac{1}{4} \left( \tfrac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda) \right) \tilde{z}^2 
+ \tfrac{1}{2} \tfrac{\Lambda \sqrt{\Lambda^2 - 4(1 - \lambda)^2}}{\sqrt{1 - \lambda} \sqrt{\Lambda^2 + 4 \lambda (1 - \lambda}} \tilde{z}^3 + o(\tilde{z}^4) \Big],
\label{eq:potential_teylor_2}
\end{equation}
%
where $\tilde{z} = z - z_{max}$.
It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs. \ref{pic:action_period_2}, \ref{pic:temperatures_2}, and summarize our results on the Fig. \ref{pic:phase_boundary_combined}.
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/action_period_2nd_order_transition_b2.eps}}
\caption{\dots}
\label{pic:action_period_2}
\end{figure}
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_temperatures_b2.eps}}
\caption{\dots}
\label{pic:temperatures_2}
\end{figure}
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
\caption{\dots \label{pic:phase_boundary_combined}}
\end{figure}
%
